Title

### 2024-08-30 paper.tex
mostly finish future work section

\section{Future work}
The paper (TODO: cite) describes a correspondence between Steinberg variety and pairs of young tableaux.  
We observe that \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something liek the stienber variety.
Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of yound tableaux: one of shape of \(X\), one of shape of \(A_{X, a, b}\).
\par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

>>>>

\section{Future work}
The paper (TODO: cite) describes a bijection between the Steinberg variety (which is blah) and pairs of standard Young tableaux (each having shape blah).
The variety \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) looks something like the Steinberg variety.
Maybe there is a similar correspondence, between elements of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) and pairs of standard Young tableaux: one having the shape of the Jordan form of \(X\), one having the shape of the Jordan form of \(A_{X, a, b}\).
\par Separately, this paper could use a nice introductory section where we motivate the study of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
